Issue

Communication between team members was less than ideal this iteration. We struggled to complete some parts of the assigned work, and we were uncertain as to what had actually been completed by each other. This left the project in a state of limbo for a while.

The program's component architecture is still incomplete. This has hampered the building of our test harness.

Our test harness is incomplete.


Improvement Actions

We must learn to organise our time better, and to collaborate better. Perhaps trac tickets are an approriate way to manage what is yet to be completed here. We have a Trac plugin which allows us to track the time spent on a part of the project by different people, which would help to manage our time more effectively.

While we have the architecture drawn out and are aware of what our interfaces should be exposing, this now needs to be written and implemented. Once we have this skeleton, it is imperative that we develop our test harness to check our actual implementation against. Naturally, setting this foundation and building the test harness properly should now be the first step in our implementation iteration.

Because we have no structure to our test harness, we must take care to make sure that the program is constructed properly and build our test harness at the earliest possible point in time.


Successes from previous iteration

I have recapped much of what I forgot regarding subversion and can now contribute to the project's codebase properly again. 
Unfortuantely, the test harness we identified needed implemeting in the last report has not been successfully built. However, the project is more easily testable and we have made headway in our work with Jenkins, pitest, and others. 
We have been generally successful when improving on problems identified in the previous report.
